Data for ms. 1

### 2017-05-02 ms1/ms1.Rmd
plr

all_condition_model = function(bene) {
  f = formula(paste0('n_claims ~ age + is_female + n_visits + ', paste0(conditions, collapse=' + ')))
  start = rep(0.1, length(all.vars(f)))
  filter(bene, age >= 67) %>%
    glm(f, family=quasipoisson(link='identity'), start=start, data=.) %>%
    tidy
}

```

@@

```{r fig1_claims_by_age}
# Show three lines: claims among all beneficiaries, among those with no ccs,
# and those with no OP visits. Exclude the no_cc, age=66 datapoint, which is
# artificially high.
claims_by_age %>%
  filter(year==2011, !(group=='no_cc' & age < 67)) %>%
  ggplot(aes(x=age,
             y=mean_n_claims,
             ymin=mean_n_claims-sem_n_claims,
             ymax=mean_n_claims+sem_n_claims,
             color=group)) +
  geom_point() +
  geom_linerange() +
  theme_minimal() +
  scale_x_continuous(breaks=c(66, 70, 80, 90, 96))
```

```{r fig1_cc_by_age}
claims_by_age %>%
  filter(year==2011, age >= 67) %>%
  ggplot(aes(x=age,
             y=mean_n_cc,
             ymin=mean_n_cc-sem_n_cc,
             ymax=mean_n_cc+sem_n_cc)) +
  geom_point() +
  geom_linerange() +
  theme_minimal() +
  scale_x_continuous(breaks=c(67, 70, 80, 90, 96)) +
  ylim(0, 6)
```

```{r visits_by_age}
claims_by_age %>%
  filter(year==2011) %>%
  ggplot(aes(x=age,
             y=mean_n_visits,
             ymin=mean_n_visits-sem_n_visits,
             ymax=mean_n_visits+sem_n_visits)) +
  geom_point() +
  geom_linerange() +
  theme_minimal() +
  scale_x_continuous(breaks=c(66, 70, 80, 90, 96))
```

>>>>

all_condition_model = function(bene) {
  f = formula(paste0('n_claims ~ age + is_female + n_visits + ', paste0(conditions, collapse=' + ')))
  start = rep(0.1, length(all.vars(f)))
  filter(bene, age >= 67) %>%
    glm(f, family=quasipoisson(link='identity'), start=start, data=.) %>%
    tidy
}
```

@@

```{r fig1_claims_by_age}
# Show three lines: claims among all beneficiaries, among those with no ccs,
# and those with no OP visits. Exclude the no_cc, age=66 datapoint, which is
# artificially high.
claims_by_age %>%
  filter(year==2011, !(group=='no_cc' & age < 67)) %>%
  ggplot(aes(x=age,
             y=mean_n_claims,
             ymin=mean_n_claims-sem_n_claims,
             ymax=mean_n_claims+sem_n_claims,
             color=group)) +
  geom_smooth(method='lm', se=F, size=0.5) +
  geom_point() +
  geom_linerange() +
  theme_minimal() +
  scale_x_continuous(breaks=c(66, 70, 80, 90, 96))
```

```{r fig1_cc_by_age}
claims_by_age %>%
  filter(year==2011, age >= 67, group != 'no_cc') %>%
  ggplot(aes(x=age,
             y=mean_n_cc,
             ymin=mean_n_cc-sem_n_cc,
             ymax=mean_n_cc+sem_n_cc,
             color=group)) +
  geom_point() +
  geom_linerange() +
  theme_minimal() +
  scale_x_continuous(breaks=c(67, 70, 80, 90, 96)) +
  ylim(0, 6)
```

```{r visits_by_age}
claims_by_age %>%
  filter(year==2011, group != 'no_visits') %>%
  ggplot(aes(x=age,
             y=mean_n_visits,
             ymin=mean_n_visits-sem_n_visits,
             ymax=mean_n_visits+sem_n_visits,
             color=group)) +
  geom_point() +
  geom_linerange() +
  theme_minimal() +
  scale_x_continuous(breaks=c(66, 70, 80, 90, 96))
```
